### 2013-01-03 exercise2/paper/paper.tex
moved and edited paper

@@

>>>>

\section{TODO}

\begin{itemize}
\item Structure for paper
\item Implementation of cutsom bn-searcher
\item documentation of cutsom bn-searcher
\item comparison and interpretation of the results
\item description of the used R and Weka features and commands
\item description of the setup/infrastructure (weka, custom searcher, R, runtime, comparison, data set, ...)
\item R script that runs the custom searcher
\item R script that runs a default searcher
\item find and describe a custom search algorithm we want to uses
\end{itemize}

@@

\subsection{RWeka}

RWeka is a interface in R that wraps the Weka framework and has a really good documentation.

Some good stuff to know:

\texttt{WOW("at.ac.tuwien.machine\_learning.UltraSearcher")} WOW is a function in R that reads and prints all possible options of a weka class. This can be done for classifiers, filters, searchers and all other types in weka.
